A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-17 paper/paper.tex
Un-superscripted primes on variables
Removed a word that shouldn't have been there

\begin{algorithm}[t]
\DontPrintSemicolon
\nl    \For {$l \in L$}{
\nl        \bf{Let} $P^{''} \gets \{ u \in P^{'} : u \neq v \wedge A_G[v][u] = l \}$ \;
\nl        \bf{Let} $T^{''} \gets \{ u \in T^{'} : u \neq w \wedge A_H[w][u] = l \}$ \;
\nl        \If {$P^{''} \negmedspace\neq \emptyset$ \bf{and} $T^{''} \negmedspace \neq \emptyset$}{
    \nl $\AlgVar{future^{'}} \gets \AlgVar{future^{'}} + \langle P^{''}\negmedspace, T^{''} \rangle$}
       }
    \caption{Replacement for \linerangeref{NewPWithEdge}{InnerLoopEnd} of \cref{McSplitAlg} to handle directed and labelled cases.}
\label{labDirAlg}
\end{algorithm}

@@

In the CP-FC algorithm, each vertex in $v \in \V(G)$ is represented by a
variable, whose domain corresponds to the set of vertices in $\V(H)$ to which
$v$ may currently be mapped, with an additional special $\bot$ value
representing an unmapped vertex.
Given a label class $\langle P,T \rangle$ in \McSplit\, the vertices in $P$
correspond to variables in CP-FC. The label-class representation of domains is
possible because throughout the CP-FC algorithm for max common subgraph, the
domains of any two variables are either identical or disjoint (excluding
$\bot$, which is slightly more complicated). To the best of our knowledge, this
observation has not been made previously, and it is not exploited in other
implementations.

>>>>

\begin{algorithm}[t]
\DontPrintSemicolon
\nl    \For {$l \in L$}{
\nl        \bf{Let} $P'' \gets \{ u \in P' : u \neq v \wedge A_G[v][u] = l \}$ \;
\nl        \bf{Let} $T'' \gets \{ u \in T' : u \neq w \wedge A_H[w][u] = l \}$ \;
\nl        \If {$P'' \negmedspace\neq \emptyset$ \bf{and} $T'' \negmedspace \neq \emptyset$}{
    \nl $\AlgVar{future'} \gets \AlgVar{future'} + \langle P''\negmedspace, T'' \rangle$}
       }
    \caption{Replacement for \linerangeref{NewPWithEdge}{InnerLoopEnd} of \cref{McSplitAlg} to handle directed and labelled cases.}
\label{labDirAlg}
\end{algorithm}

@@

In the CP-FC algorithm, each vertex $v \in \V(G)$ is represented by a
variable, whose domain corresponds to the set of vertices in $\V(H)$ to which
$v$ may currently be mapped, with an additional special $\bot$ value
representing an unmapped vertex.
Given a label class $\langle P,T \rangle$ in \McSplit\, the vertices in $P$
correspond to variables in CP-FC. The label-class representation of domains is
possible because throughout the CP-FC algorithm for max common subgraph, the
domains of any two variables are either identical or disjoint (excluding
$\bot$, which is slightly more complicated). To the best of our knowledge, this
observation has not been made previously, and it is not exploited in other
implementations.
